Solar jet observed at the limb in SDO/SST

### 2016-08-04 paper/ms_temp_paper.tex
Fixes to the doppler slit plot.
HI SAM I AM IN YOUR COMPUTER COMMITING YOUR PAPER.

import numpy as np

import astropy.units as u
import datetime
from datetime import timedelta
from astropy.constants import c
from glob import glob

dopp_grid = texfigure.MultiFigure(2, 2, reference="Dop_Exam")

# some functions
def get_time(ind, time_0):
    current_time = time_0 + timedelta(seconds=7.7)*ind
    return current_time

@@

# read in some datas
dop_files = []
for i in range(75,90):
	dop_files.append(manager.data_file('dops/dop_arr_test0{}.npy'.format(i)))
dop_files.sort()

@@

# get the variables for the slit analysis
# lets use a perfectly horizontal slit
x1 = 45
x2 = 90
y1 = 58
y2 = 90
N = 0

dop_frames = [75,76,77,78,79,80,81,82,83]

### make the graph for time and slit
slit_inds = slit.slit_count(45, 90, 58, 90, 0, 1, N)

# index the arrays properly
inds_x = np.array([slit_inds[:,:,0]])
inds_y = np.array([slit_inds[:,:,1]])
ind_dop = dops[inds_x, inds_y, :]

dop_fin = ind_dop[0]

# get the dopplergrams associated with the rotation
slit_list = []
frames = range(79,90)
for i, n in enumerate(frames):
    temp = dop_fin[0,:,n]
    temp = temp[temp < 10*dop_fin.unit]
    slit_list.append(temp)

xy_slit = [np.array(zip(range(len(slit_inds[0])), s.value)) for s in slit_list]

slit_line =  mpl.lines.Line2D(np.array([45,58]),
                                     np.array([90,90]),
                                     linestyle='solid', color='k')

@@

# new figure using subplot2grid specificially
fig = plt.figure(figsize=(6,12))
gs = gridspec.GridSpec(3,4)
ax1 = plt.subplot(gs[0,0])
ax2 = plt.subplot(gs[0,1])
ax3 = plt.subplot(gs[0,2])
ax4 = plt.subplot(gs[0,3])
ax5 = plt.subplot(gs[1,0])
ax6 = plt.subplot(gs[1,1])
ax7 = plt.subplot(gs[1,2])
ax8 = plt.subplot(gs[1,3])
ax9 = plt.subplot(gs[2,0])
ax10 = plt.subplot(gs[2,1:])

@@

for i, an_ax in zip(dop_frames, ax_list):
    temp_dop = dops[i].value
    im = an_ax.imshow(temp_dop[:250,40:], vmax=15, vmin=-15,
             cmap='RdBu', origin='lower',
             norm=mpl.colors.SymLogNorm(1))
    im.cmap.set_under('w')
    im.cmap.set_over('w')

cb = fig.colorbar(im)
cb.set_label('Velocity {}'.format(dop_fin.unit))

@@

# fig, ax = plt.subplots()
line_segments = LineCollection(xy_slit,
                               linewidths = 0.25,
                               linestyle='solid',
                               cmap=n_cmap)

line_segments.set_array(np.arange(len(slit_list)))
ax10.add_collection(line_segments)
ax10.axis([1,10,-1.5,1.5])

ax4.add_line(slit_line)

axcb = fig.colorbar(line_segments)
axcb.set_label('Time')
ax10.set_title('Slit across')
ax10.set_xlabel('Distance across slit')
ax10.set_ylabel('Velocity {}'.format(dop_fin.unit))
plt.sci(line_segments)

dop_gird.placement = 't'
dop_grid.caption = ''

plt.draw()
plt.show()

@@

The dopplergrams demonstrated in \cref{fig:dop_grid}
Applying the method described above, we obtain dopplergrams of the feature when applied to the spectroscopic data produced by CRISP, presented in \cref{fig:dop_grid}.
The immediately apparent when we examine the data is the difficulty in clearly identifying the jet, with the complex background demonstrating shifts in both directions.
This is due top the effect of observing along the limb, we see features further round the disk as bulk motions.
The jet we are examining, apparently originates in a 'bank' of spicules, visible as lines of red shift in the image.
The initial acceleration of the spicule at $07:30$ shows no rotational motion and is infact hard to differentiate from the background.
However, the second jet formation and consequent acceleration reveal significant rotational motion.

>>>>

import numpy as np
import numpy.ma as ma

import astropy.units as u
import datetime
from datetime import timedelta
from astropy.constants import c
from sunkitsst.read_cubes import read_cubes
from glob import glob

# some funcitons
def get_time(ind, time_0):
    current_time = time_0 + timedelta(seconds=7.7)*ind
    return current_time

@@

# # read in some datas
# ha_files = glob('/storage2/jet/SST/*.npy')
# ha_files.sort()
# dop_files = glob('/storage2/jet/dop_arrs/*.npy')
# dop_files.sort()

dop_frames = [76,77,78,79,80,81,82,83,84]
frame_numbers = np.arange(75,90)

# read in some datas
dop_files = []
for i in frame_numbers:
	dop_files.append(manager.data_file('dops/dop_arr_test0{}.npy'.format(i)))
dop_files.sort()

@@

# get the variables for the slit analysis
# lets use a perfectly horizontal slit
x1 = 45
x2 = 65
y1 = y2 = 130
N = 0

### make the graph for time and slit
slit_inds = slit.slit_count(x1, y1, x2, y2, 0, 0, N)

# index the arrays properly
inds_x = np.array([slit_inds[:,:,0]])
inds_y = np.array([slit_inds[:,:,1]])
ind_dop = dops[:,inds_y, inds_x]

dop_fin = ind_dop[:,0]

# get the dopplergrams associated with the rotation
slit_list = []
for i, n in enumerate(frame_numbers):
    temp = dop_fin[i]
    temp[temp > 20*dop_fin.unit] = np.NaN
    slit_list.append(temp)

xy_slit = [np.array(zip(range(len(slit_inds[0])), s[0].value)) for s in slit_list]

@@

# new figure using subplot2grid specificially
fig = plt.figure(figsize=texfigure.figsize(pytex, height_ratio=1.3, figure_width_context='textwidth'))
gs = gridspec.GridSpec(3,8)
ax1 = plt.subplot(gs[0,0:2])
ax2 = plt.subplot(gs[0,2:4])
ax3 = plt.subplot(gs[0,4:6])
ax4 = plt.subplot(gs[0,6:8])
ax5 = plt.subplot(gs[1,0:2])
ax6 = plt.subplot(gs[1,2:4])
ax7 = plt.subplot(gs[1,4:6])
ax8 = plt.subplot(gs[1,6:8])
ax9 = plt.subplot(gs[2,0:2])
ax10 = plt.subplot(gs[2,3:])

@@

for n, an_ax in zip(dop_frames, ax_list):
    i = np.where(frame_numbers == n)[0][0]
    time_dop = get_time(n, t0_dop).strftime('%H:%M:%S')
    temp_dop = dops[i].value
    y_shift = 40
    im = an_ax.imshow(temp_dop[:250,40:], vmax=15, vmin=-15,
                      cmap='RdBu', origin='lower',
                      norm=mpl.colors.SymLogNorm(1),
                      interpolation='none')
    an_ax.plot([x1, x2], [y2-y_shift,y2-y_shift], color='k')
    an_ax.set_title('{}'.format(time_dop), fontsize=10)
    an_ax.set_xlim(left=1, right=80)
    an_ax.set_ylim(bottom=1, top=225)
    an_ax.locator_params(axis='x', nbins=4)
    im.cmap.set_under('w')
    im.cmap.set_over('w')

cb = fig.colorbar(im, ax=ax9, pad=0.1)
cb.set_label('Velocity {}'.format(dop_fin.unit._repr_latex_()))
cb.set_ticks([-15,-9,-6,-3,-2,-1,0,1,2,3,6,9,15])

@@

# fig, ax = plt.subplots()
line_segments = LineCollection(xy_slit,
                               linewidths = 0.5,
                               linestyle='solid',
                               cmap=n_cmap)

line_segments.set_array(np.arange(1,len(slit_list)+1))
ax10.add_collection(line_segments)
ax10.axis([1,xy_slit[0].shape[0]-1,-1.6,1.6])
ax10.axhline(0, color='k', linewidth=0.5)

axcb = fig.colorbar(line_segments)
axcb.set_label('Frame Number')
axcb.set_ticks(range(1, len(xy_slit)+1))
#ax10.set_title('Slit across')
ax10.set_xlabel('Distance Along Slit [pixels]')
ax10.set_ylabel('Velocity {}'.format(dop_fin.unit._repr_latex_()))
plt.sci(line_segments)

gs.tight_layout(fig, w_pad=0.2, pad=4)

dop_grid = manager.save_figure('dop-exam', fig)
dop_grid.figure_width = r'\textwidth'
dop_grid.placement = 't'
dop_grid.caption = ''

@@

The dopplergrams demonstrated in \cref{fig:Dop_Exam}
Applying the method described above, we obtain dopplergrams of the feature when applied to the spectroscopic data produced by CRISP, presented in \cref{fig:Dop_Exam}.
The immediately apparent when we examine the data is the difficulty in clearly identifying the jet, with the complex background demonstrating shifts in both directions.
This is due top the effect of observing along the limb, we see features further round the disk as bulk motions.
The jet we are examining, apparently originates in a 'bank' of spicules, visible as lines of red shift in the image.
The initial acceleration of the spicule at $07:30$ shows no rotational motion and is infact hard to differentiate from the background.
However, the second jet formation and consequent acceleration reveal significant rotational motion.
